Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-03-30 manuscript.Rmd
added fresh spectra; wrote bootstrap draft function; other changes

DAL$Label = "DAL"
TSK$Label = "TSK"
MFM$Label = "MFM"
```

<!-- PRE-PROCESS DATA -->
```{r}
if (!hasName(DAL, "sg2")) {
  source(here("R","pre_process.R"))
}
```

>>>>

if (file.exists(here("data","output","fresh_spectra.rds"))) {
  FRE = readRDS(here("data","output","fresh_spectra.rds"))
} else {
  source(here("R","read_data.R"))
  read_data_fresh()
  FRE = readRDS(here("data","output","fresh_spectra.rds"))
}

FRE$Label = "FRE"
DAL$Label = "DAL"
TSK$Label = "TSK"
MFM$Label = "MFM"
```

<!-- PRE-PROCESS DATA -->
```{r}
if (!hasName(DAL, "emsc")) {
  source(here("R","pre_process.R"))
}
```
